### 2020-06-10 latex/vlp.tex
Finalize the first skeleton of the thesis
This commit finishes the skeleton of the thesis, with all sections and
headings as desired. There is currently no content here.
First version of the VLP energy-gain theorem

%/========== Variable Length Pendulum ==========/%
\section{The Variable Length Pendulum}\label{sec:vlp}

%/========== /Variable Length Pendulum ==========/%
% vim: set ts=3 sw=3 sts=0 et ffs=unix :

>>>>

%/========== Variable Length Pendulum ==========/%
\chapter{Application of VNHCS: The Variable Length Pendulum}\label{sec:vlp}
\section{Motivation}
% TODO: Why is this a good problem to study? What is the problem? What would a human do on a standing swing?
\section{The VLP Constraint}
% TODO: Go through the development of the constraint and prove it gains energy

\begin{thm}
For the variable-length pendulum, define \(\theta := \arctan_2(p,q)\). 
A VNHC of the form \(l = l(\theta)\) injects energy if there exists \(l_{avg} \in \R_{>0}\) such that
\[
   \left(l(\theta) - l_{avg}\right)sin(2\theta) \leq 0 \text{ }\forall \theta \in \mathbb{S}^1
\]
with the property that the inequality is strict for almost every \(\theta\).
\end{thm}
\begin{proof}
    Choose, as a candidate anti-Lyapunov function, the energy for the average-length pendulum 
    \[
       E_{avg}(q,p) := \frac{1}{2}\frac{p^2}{m l_{avg}^2} 
                    + m g l_{avg} (1-\cos(q))
    \]

    which is non-negative and has derivative 
    \[
      \dot{E}_{avg} = \frac{-g\sin(q)p \left(l(\theta)^3 - l_{avg}^3\right)}
                 {l_{avg}^2l(\theta)^2}
    \]

    We will show that \(E_{avg}\) is increasing.

    % VBOX UNDERFULL WARNING HERE, IGNORE IT
    Observe that \(\sign{\sin(q)p} = \sign{\sin(2\theta)}\) and, 
    by Lemma \textbf{TODO: REF LEMMA},
    \( \sign{l(\theta)^3 - l_{avg}^3} 
     = \sign{ l(\theta) - l_{avg}}\).

     Then the derivative of \(E_{avg}\) is almost always positive, since
     \begin{align*}
        \label{eq:}
        \sign{\dot{E}_{avg}} &= \sign{-\sin(q)p \left(l(\theta)^3 - l_{avg}^3\right)} \\
                    &= -\sign{\sin(2\theta) \left(l(\theta) - l_{avg}\right)} \\
                    &\geq 0 \text{ (by assumption)}
     \end{align*}

      Hence, \(E_{avg}\) is an anti-Lyapunov function with positive derivative,  
      so the variable-length pendulum is gaining energy.
\end{proof}

\section{Simulation Results}

%/========== /Variable Length Pendulum ==========/%
% vim: set ts=3 sw=3 sts=0 et tw=80 ffs=unix :
